Software Defect Prediction: Review, Commentary, and Recommendations

### 2015-12-16 paper/paper.tex
Push paper from sharelatex edited by all members

% DOI
\doi{10.475/123_4}

% ISBN
\isbn{123-4567-24-567/08/06}

%Conference
\conferenceinfo{PLDI '13}{June 16--19, 2013, Seattle, WA, USA}

\acmPrice{\$15.00}

%
% --- Author Metadata here ---
\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{Software Defect Prediction: Review, Commentary, and Future Work}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{3} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Matthew Neal\\
       \affaddr{Department of Computer Science}\\
       \affaddr{North Carolina State University}\\
       \affaddr{Raleigh, North Carolina, USA}\\
       \email{meneal@ncsu.edu}
% 2nd. author
\alignauthor
Joseph Sankar\\
	   \affaddr{Department of Computer Science}\\
       \affaddr{North Carolina State University}\\
       \affaddr{Raleigh, North Carolina, USA}\\
       \email{jesankar@ncsu.edu}
% 3rd. author
\alignauthor Alexander Sobran\\
       \affaddr{Department of Computer Science}\\
       \affaddr{North Carolina State University}\\
       \affaddr{Raleigh, North Carolina, USA}\\
       \email{aisobran@ncsu.edu}
\and  % use '\and' if you need 'another row' of author names
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

\maketitle
\begin{abstract}
This paper provides a comprehensive review and commentary on software defect prediction research. Review and criticism of previous work is presented. Future steps in the domain are given.
\end{abstract}

@@

\section{Introduction}
It is a well-known fact that software bugs are much cheaper and easier to fix before being released. But finding these bugs is often difficult and may not be cost effective to fix. Researchers have been working on fault detection models to predict which software modules are most likely to contain bugs post-release. Management can use these predictions to focus testing and bug-fixing efforts on those modules, resulting in fewer bugs in release which are less costly to fix.

In this paper, we focus on the advances made in software fault prediction models in the literature. Section 2 contains an assortment of existing work in the area.

@@

@@

Also within the area of cross-project defect prediction, Nam et al \cite{Nam} found that when the source and target projects have a different feature distributions, the resulting model gives poor performance. The authors use Transfer Component Analysis (TCA) to find a common feature set for both projects and then map the data of both projects to it. They found that TCA is sensitive to normalization, so they developed an improvement, TCA+ to select appropriate normalization options. After using TCA+ to create cross-project defect prediction models for eight open-source projects, they found a significant improvement in prediction performance compared to traditional algorithms and techniques. The authors proposed applying knowledge in one domain to another to further improve performance.

@@

@@

Every fault prediction study used some sort of machine learning algorithm as the heart of the model. There are a variety of ML algorithms including regression, neural networks, support vector machines, and decision trees.

\subsection{Regression}
Regression is a ML algorithm for data that can be fitted to a curve. A total of X papers use some form of regression (\cite{Posnett}, \cite{Rahman}, ...). Regression algorithms are considered to be the simplest type, but can perform well if the data can be well fitted to some sort of line or curve.

\subsection{Neural Networks}
Neural networks are designed to model the learning pattern of the human brain. Essentially, neural networks consist of nodes connected by links. The more a link is activated during training, the stronger it becomes and the more likely it will be selected during testing.

Jun Zheng \cite{zheng2010} used a back propagation neural network (BPNN) with AdaBoost, a way to achieve better classification results by producing diverse base classifiers. Zheng states that he used neural networks because they are popular in pattern recognition and BPNNs because they were the most frequent neural network used in the literature. AdaBoost was chosen because it is a popular way to improve the performance of the model.

\subsection{Other ML Algorithms}
Vandecruys et al \cite{Vandecruys} used a novel algorithm known as AntMiner+, which is based on Ant Colony Optimization which models the foraging behavior of ant colonies.

@@

Nam et al \cite{Nam} implemented TCA+, which is a novel feature extraction technique for transfer learning with improved normalization.

\subsection{Discussion}
Catal et al \cite{Catal} suggested that more models be based on machine learning techniques rather than statistical methods or expert based systems. We see that research has followed the advice of the authors. Arisholm et al \cite{Arisholm} did not find any major differences among the different machine learning techniques, although they found that C4.5 with Adaboost gave the best results.

@@

The use of confusion matrices, and the metrics (precision, recall, and F-measure) that revolve around them are very common in the fault prediction area.  As will likely be known by the reader, a confusion matrix is a summary of predicted values compared with actual values.  A confusion matrix in most cases will have been created based on test data where the actual values are known.  Precision, recall, and F-Measure are all statistics that can be used to assess how close a model has come in predicting the actual on the test data.  This methodology is used in nearly all of the papers we read \cite{Posnett} \cite{Nam} \cite{Bird} \cite{Vandecruys} \cite{Nagappan} \cite{Arisholm} \cite{Rahman} \cite{Jiang}.

Even though the methodology is fairly standard throughout the papers we read, what actual metric is reported between precision, recall, overall accuracy, and F-Measure has considerable variance between papers.  The Vandecruys paper \cite{Vandecruys} even uses terminology that is separate from many other publications in using sensitivity for recall and specificity for the true negative rate, which is a seldom reported statistic. One suggestion in \cite{Hall} is to present the confusion matrix itself rather than to present one statistic or the other when possible (where possible is determined by the sheer number of confusion matrices that would be produced).  The idea is that it would better enable comparison across studies since researchers could produce whatever statistic they happen to need from the data itself.

@@

The ROC curve is another fairly standard metric for performance used in the literature.  ROC, or Receiver Operating Characteristic analysis is an elaboration of the confusion matrix approach.  The idea is to use the rates of false positives and true positives on an x-y plane and to have x values represent the rates of false positives, and y values represent the rates of true positives.  The rate for a particular model can be plotted as point on the ROC curve and the area under the curve (AUC) be used as a metric to determine the quality of the model with a point at (0,1) being optimal \cite{Posnett}.

These methods are used in a few of the papers we reviewed \cite{Rahman} \cite{Arisholm} \cite{Posnett}.  Some negatives have been pointed out about the ROC approach and it's usefulness in certain circumstances.  One such negative is the fact that ROC curve approaches have "an overly optimistic view of an algorithm's performance if there is a large skew in the class distribution".  \cite{Davis}  Other papers mention the fact that both ROC/AUC approaches and confusion matrix based approaches in general do not address the whether a particular fault prediction methodology can pinpoint the source of the faults or not.  Since knowing where to find errors is just as important or more important than knowing whether errors exist or not several papers find ROC/AUC insufficient as an evaluation metric \cite{Posnett} \cite{Arisholm} \cite{Rahman}.

@@

The basic idea of the metric is a set of two curves on an x-y plane that has a percentage of faults as the y-axis, and the percentage of the lines of code included in classes selected to focus verification as the x-axis.  Classes are ranked according to their likelihood of having defects, first by the model, and next by the size of the class in case of ties.  The graph has a baseline of $y=x$ which is essentially the assumption that the percentage of faults will be equivalent to the percentage of lines of code inspected, this is done using a random ranking of the classes.  On the same graph is the cost effectiveness curve which is the actual percentage of faults given the percentage of LOC of class selected to focus verification according to the ranking determined by the model.

 Arisholm et al use an area calculation that is normalized to be a proportion of the optimal area under the curve.  To find an approximation of the optimal cost effectiveness they use a ranking that puts the most error filled classes towards the front and then create a cost effectiveness line according to that ranking.  The actual calculation is\\ $CE_{\pi} = (CE_{pi}(model) - CE_{pi}(baseline))/$\\ $(CE_{pi}(optimal) - CE_{pi}(baseline))$  Other papers have used a simpler calculation of the area under the cost effectiveness curve, or AUCCE \cite{Posnett}.  The same concept is also used by Rahman et al under the name AUCEC \cite{Rahman}.

@@

\subsection{Discussion}
It seems that Arisholm's contribution to the community with Cost Effectiveness back in  2010 has provided a better metric to evaluate fault prediciton models going forward.  Seeing as the point of fault prediction should be to build tools that can be used in the real world for real projects injecting the realism that CE brings to the table seems to be totally appropriate in going forward.  Even though that is viewed as the case by some in the community confusion matrix based approaches and the related ROC curve concept are seemingly going nowhere.  These approaches will continue to be important in evaluating models until something better comes along.

@@

This section could also be labeled metrics, as it is in many places throughout the literature on this topic, but to not confuse it and the previous section on evaluation metrics we have chosen to label it features.  The main reasoning for this is the fact that metrics are actually used as features in this area and not actually as metrics for comparison of one method versus another.  The Radjenovic paper \cite{Radjenovic} is a fairly exhaustive paper with relation to metrics/features in fault prediction.  Radjenovic came up with three categories to discuss in their literature review, and we will stick with those same categories in relation to the papers we reviewed.  The categories are: Traditional, Object-Oriented, and Process.  Some of the papers we reviewed defy this categorization and use metrics that are either one offs or are hybridized to such a degree that they should be explained on their own.

@@

These are metrics that relate to complexity (ie McCabe or Halstead calculations) and lines of code.  A good number of papers we reviewed used these metrics as feature \cite{Posnett} \cite{Vandecruys} \cite{Bird}.  There is considerable discussion in terms of whether these sorts of metrics provide good quality models or not.  Hall et al indicate that in their review that models using only static code metrics that are complexity based have poor performance, but that Lines of Code based models tend to be useful \cite{Hall}.  Radjenovic et al indicate that LOC has no strong evidence behind it in terms of faults furthermore they state that smaller studies in general have given more weight to LOC and size metrics than larger studies, because of that they rated the effectiveness of the metric as "moderate"\cite{Radjenovic}.  On complexity metrics Radjenovic states that these metrics are reasonable, but that "others are better"\cite{Radjenovic}.

@@

Object oriented metrics seem to have been dominated by the metrics presented by Chidamber and Kemerer \cite{Chidamber} \cite{DAmbros}.  These metrics include things like number of children(NOC), coupling between classes (CBO), or lack of cohesion of methods (LCOM).    Object oriented metrics were used in only one of our papers, Arisholm et al, and used there really only as a comparison metric\cite{Arisholm}.  In terms of evaluation of their success or failure Radjenovic et al indicate that OO metrics are useful but that there is some debate about whether OO metrics and size are correlated and that further work is needed in that area  \cite{Radjenovic}.  Hall et al state that OO and LOC are actually on pretty equal footing and that OO provides better performance than source code metrics \cite{Hall}.

@@

Process metrics relate to things like number of developers, code churn, number of commits, features, etc.  Process metrics are mostly mined from source code management systems like Git, and also bug tracking and issue tracking systems like Jira.   These metrics have a strong following in the fault prediction community and are well represented in our papers \cite{Posnett} \cite{Bird} \cite{Arisholm} \cite{Rahman}.  Rahman et al particularly only used a set of process metrics while the other papers mentioned used some sort of combination of process and other metrics.  There is some dispute between Radjenovic and Hall with regards to process metrics, with Hall suggesting that their performance was the worst out of everything they had examined where Radjenovic considers process metrics to be promising and that they are deserving of further study and validation while additionally stating that they provide superior post-release fault prediction \cite{Hall} \cite{Radjenovic}.

\subsection{Organizational Structure}
This is an approach that was proposed by Nagappan et al at Microsoft Research \cite{Nagappan}.  The metrics included a set of 8 measures of organizational complexity: Number of engineers, Edit Frequency, Depth of Master Ownership, Percentage of Org contributing to development, Overall Organization Ownership, and Organization Intersection Factor.  They used these metrics to create a fault prediction model and compared its performance in Precision and recall against a set of OO, Traditional, and Process metrics.  For Windows Vista they show that Organizational metrics are superior to the other types of metrics available.  As mentioned in the paper there are questions about whether this approach would work outside Microsoft or with a smaller project.

Naggapan and Bird produced another paper in the next year using organizational metrics again with a bit of a twist in looking at whether distributed development had an effect on software quality \cite{Bird}.  This paper added an additional metric of the actual location of the members of teams working on Windows Vista with levels starting at the same building and growing to the point of developers working at locations across the globe from one another.  Organizaitonal metrics as well as a set of process and traditional metrics were used in conjunction with the distribution metric seemingly out of surprise that there was little difference between distributed projects and more local projects.  The idea was to try to prove that there was not in fact some correlation between the other metrics they looked at and the performance of teams across long distances.  They found that in fact there was no difference and that distributed development within one company was possible without sacrificing quality.

>>>>

% DOI
%\doi{10.475/123_4}

% ISBN
%\isbn{123-4567-24-567/08/06}

%Conference
%\conferenceinfo{PLDI '13}{June 16--19, 2013, Seattle, WA, USA}

%\acmPrice{\$15.00}

%
% --- Author Metadata here ---
%\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{Software Defect Prediction: Review, Commentary, and Recommendations}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{3} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Matthew Neal\\
       \affaddr{Department of Computer Science}\\
       \affaddr{North Carolina State University}\\
       \affaddr{Raleigh, North Carolina, USA}\\
       \email{meneal@ncsu.edu}
% 2nd. author
\alignauthor
Joseph Sankar\\
	   \affaddr{Department of Computer Science}\\
       \affaddr{North Carolina State University}\\
       \affaddr{Raleigh, North Carolina, USA}\\
       \email{jesankar@ncsu.edu}
% 3rd. author
\alignauthor Alexander Sobran\\
       \affaddr{Department of Computer Science}\\
       \affaddr{North Carolina State University}\\
       \affaddr{Raleigh, North Carolina, USA}\\
       \email{aisobran@ncsu.edu}
%\and  % use '\and' if you need 'another row' of author names
}
% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

\maketitle
\begin{abstract}
This paper provides a comprehensive review and commentary on software defect prediction research. Review and criticism of previous work is presented. Recommendations and future steps in the domain are given.
\end{abstract}

@@

\section{Introduction}
It is a well-known fact that software bugs are much cheaper and easier to fix before being released. But finding these bugs is often difficult and some bugs may be cheaper to fix than others. Researchers have been working on fault detection models to predict which software modules are most likely to contain bugs post-release. Management can use these predictions to focus testing and bug-fixing efforts on those modules, resulting in fewer bugs in release which are less costly to fix.

In this paper, we focus on the progress of software fault prediction models in the literature within the last few years. Section 2 contains an assortment of existing work in the area. We analyze the literature through different perspectives in Sections 3 through 10. Finally, in section 11, we give our overall observations and suggestions for future research in this area.

@@

A couple of years later, Hall et al \cite{Hall} performed another comprehensive literature review on fault prediction performance from January 2000 to December 2010. They hoped to see how the context, independent variables, and modeling techniques affected the performance of fault prediction models. They found that simpler modeling techniques seemed to perform better, along with feature selection on sets of independent variables. They encouraged future studies to better report their context, methodology, and performance.

A couple of years after the Hall paper was published, Radjenovic et al \cite{Radjenovic} performed a literature review of metrics used in fault prediction models. The date range of papers was about double that for the Hall paper, from 1991 to 2011. The authors found that there are major differences between the metrics used, and that object-oriented and process metrics seemed to be better at predicting faults than static code metrics.

@@

Also within the area of cross-project defect prediction, Nam et al \cite{Nam} found that when the source and target projects have different feature distributions, the resulting model gives poor performance. The authors use Transfer Component Analysis (TCA) to find a common feature set for both projects and then map the data of both projects to it. They found that TCA is sensitive to normalization, so they developed an improvement, TCA+ to select appropriate normalization options. After using TCA+ to create cross-project defect prediction models for eight open-source projects, they found a significant improvement in prediction performance compared to traditional algorithms and techniques. The authors proposed applying knowledge in one domain to another to further improve performance.

@@

Two common approaches to evaluating defect prediction models are precision-recall and ROC curves. Davis et al \cite{Davis} showed that there exists a deep connection between the two. Additionally, they claimed that ROC curves are overly optimistic with highly skewed data, and that PR curves are better suited for that type of data. While there exists a connection between the two types of curves, the authors showed that an algorithm that optimizes the area under the ROC curve does not necessarily optimize the area under the PR curve. Essentially, they were trying to show that although both evaluation methods are related, just one does not show the complete picture. Both are needed to gain a better understanding of the performance of an optimization algorithm.

Given that managers are trying to improve the process of software development, how do we best manage such a process? Chidamber and Kemerer \cite{Chidamber}
developed and evaluated six such metrics. They were then tested at two different sites via automated tools. The authors concluded by suggesting how these metrics can be adapted in a software development environment and correlated with managerial performance indicators.

D'Ambros et al \cite{DAmbros} presented a benchmark for fault prediction. Their motivation was the observation that such a benchmark did not exist, making it difficult to compare the models and approaches found in the literature. Their benchmark consisted of a publicly available data set consisting of five software systems. They also compared and evaluated well-known fault prediction methods and developed some new ones. They then ran their new methods on their benchmark, finding that they actually performed the best out of all. They conclude by stating that techniques based off of only one metric do not work well against every software project, meaning that the more useful metrics included, the better.

Kim et al \cite{Kim} introduced a new technique called \textit{Change Classification}, which looks at individual changes to source code and predicts whether those changes are similar to previous buggy or clean changes. When testing on twelve open-source systems, change classification was found to be as accurate as other leading bug prediction techniques. Since this was a new technique, there were a number of open issues for future research.

Wu et al \cite{Wu} implemented an algorithm which recovers links between bugs and committed changes called \textit{ReLink}. The authors tested this new algorithm on three open-source projects, finding that it was roughly as accurate as traditional heuristics.

Zhang et al \cite{Zhang2014} attempted to implement a universal defect prediction model, which would work on both new projects and projects with historical data. In order to account for variations in the distributions of predictors, the authors clustered projects based on the similarities of the predictors. Their dataset included almost 1,400 open-source projects. They found their universal model performs well on both within-project and cross-project models. They have hope that such a universal model is achievable.

\section{Ecological Inference}
Ecological inference or EI was presented in the first paper we reviewed, the Posnett paper \cite{Posnett}.  Posnett et al explain ecological inference as the idea that an observation or finding at an aggregated level can apply at a disaggregated level.  For example, the idea that a model of defects at the package level also applies at the file level.

The suggestion is that in the fault prediction area there is in fact an Ecological Fallacy, where findings at the aggregated level are expected to be valid at a disaggregated level.  As in the example above a defect model that is created at a package level is applied to predict defects at a file level. Based on this concept Posnett wanted to prove whether or not the Ecological Fallacy applied to fault prediction.

Posnett et al posit two main overarching conclusions in their paper:  That aggregated models when evaluated only at the aggregated level may have deceivingly strong performance, and furthermore inferences from aggregated models may not apply to their disaggregated parts \cite{Posnett}.  Posnett cites another of our papers, Bird et al, as a potential rebuttal of his results because of the fact that geographical distribution did not have an effect in Bird's study \cite{Bird}.

Moving beyond the Posnett paper, Rahman et al in 2012 made considerations regarding the aggregation level of their models, in that they decided to examine code at the file level.  Rahman et al went that direction because they were worried that evaluation of a model on a coarser level of aggregation may not be a good predictor at the file level \cite{Rahman}.  Rahman again cites Ecological Inference in a 2013 paper on Process Metrics as a threat for validity \cite{Rahman13}.

\subsection{Discussion}
The main question is whether EI and EF represent important concepts to researchers going forward in the fault prediction area.  It seems that only a subset of papers are actually being written currently where EF is recognized as a concern.  Our recommendation would be further study to validate Posnett's 2011 work, and if the work is further validated the community should consider EI/EF when conducting studies.

@@

Every fault prediction study leverages a machine learning algorithm as the heart of the model. Machine learning algorithms are a way to "learn" from data and create a model that can make predictions. Typically, there is a set of training data which the algorithm uses to generate the model. Then, it is evaluated with test data to see if it generates accurate and reliable predictions. There are a variety of ML algorithms including regression, neural networks, support vector machines, and decision trees.

\subsection{Regression}
Regression is a ML algorithm for data that can be fitted to a curve. Regression algorithms are considered to be the simplest type, but can perform well if the data is a well-fit to some sort of well-behaved mathematical function. Most of the referenced papers used some form of regression as their main algorithm (\cite{Posnett}, \cite{Bird}, \cite{Nagappan}, \cite{Rahman}).

\subsection{MARS}
MARS is short for Multivariate Adaptive Regression Splines.  The concept goes back to a 1991 paper by Friedman the technique is a non-parametric method used to model complex multivariate non-linear scenarios.  It is suited modeling non-linear data because of the fact that models have a series of hinge and basis functions.  Each hinge function per Bettenburg et al "partitions the data into disjoint regions that can be described separately"\cite{Bettenburg}.  Bettenburg et al used MARS in building models to look at the difference between global and local trained model.  The Jiang paper used MARS models based on Bettenburg's work as a baseline to compare PCC and PCC+ models against \cite{Jiang}.

\subsection{Neural Networks}
Neural networks are a family of machine learning algorithms based initially on the perceptron. The basic structure of neural network consist of an input layer, layers of activation functions, and an output layer. Each layer is connected to other layers but no connections exist within the layer. The result of each activation function is delivered to the next connected layer until it finally reaches an output layer.

Jun Zheng \cite{zheng2010} used a back propagation neural network (BPNN) with AdaBoost, as a way to achieve better classification results by producing diverse base classifiers. Zheng states that he used neural networks based on their popularity in pattern recognition, and BPNNs because they were the most frequent neural network used in the literature. AdaBoost was chosen because it is a popular way to improve the performance of the model.

\subsection{Naive Bayes}
Zhang et al \cite{Zhang2014} use Naive Bayes classifier as a modeling technique in their approach to build a universal defect prediction model for cross-project defect prediction. They decided on this classifier because previous research determined that Bayes learners outperform other learners when predicting defects in noisy data. The Naive Bayes classifier is based on Bayes' theorem with independence assumptions.

\subsection{Probabilistic Graphical Models}
Probabilistic graphical models are considered powerful machine learning tools. They consist of a graphical structure where nodes are events and edges are conditional dependencies. Some examples include bayesian networks and hidden markov models. They have many strength including informative visualization from structures, insights from model inference, and lower complexities. Inferring insights from model structure could be leveraged in software defect prediction. Certain conditional relationships can be reported verbally to all concerned parties. It has also been posited every machine learning algorithm is an instance of a probabilistic graphical model.\cite{Bishop:2006:PRM:1162264}

\subsection{Other ML Algorithms}
Vandecruys et al \cite{Vandecruys} used a novel algorithm known as AntMiner+, which is based on Ant Colony Optimization(ACO) which models the foraging behavior of ant colonies. In AntMiner+, ACO is used to optimize a rule based classification algorithm. Rule based classification algorithms usually have greater comprehensibility than other machine learning algorithms as the association rules can be reported. Vandecruys also presented good accuracy using AntMiner+.

@@

\subsection{Discussion}
Catal et al \cite{Catal} suggested that more models be based on machine learning techniques rather than statistical methods or expert based systems. We see that research has followed the advice of the authors. Among them, Arisholm et al \cite{Arisholm} did not find any major differences among the different machine learning techniques, although they found that C4.5 with Adaboost gave the best results.

@@

The use of confusion matrices, and the metrics (precision, recall, and F-measure) derived from them are very common in the fault prediction area.  As will likely be known by the reader, a confusion matrix is a contingency table summarizing the predicted values compared with actual values.  A confusion matrix in most cases will have been created based on test data where the actual values are known.  Precision, recall, type I errors, type II errors, and F-Measure are all statistics that can be used to assess how close a model has come in predicting the actual on the test data.  This methodology is used in nearly all of the papers we read \cite{Posnett} \cite{Nam} \cite{Bird} \cite{Vandecruys} \cite{Nagappan} \cite{Arisholm} \cite{Rahman} \cite{Jiang} \cite{Zhang2014}

Even though the methodology is fairly standard throughout the papers we read, what actual metric is reported between precision, recall, overall accuracy, type I errors, type II errors, and F-Measure has considerable variance between papers.  The Vandecruys paper \cite{Vandecruys} even uses terminology that is separate from many other publications in using sensitivity for recall and specificity for the true negative rate, which is a seldom reported statistic. One suggestion in \cite{Hall} is to present the confusion matrix itself rather than to present one statistic or the other when possible (where possible is determined by the sheer number of confusion matrices that would be produced).  The idea is that it would better enable comparison across studies since researchers could produce whatever statistic they happen to need from the data itself.

Another measurement we encountered is the g-measure. It is used by Zhang et al \cite{Zhang2014} in their cross-project defect prediction study. They use it to combat the the instability of precision in datasets with low percentages of defects.

@@

The ROC curve is another fairly standard metric for performance used in the literature.  ROC, or Receiver Operating Characteristic analysis is an elaboration of the confusion matrix approach.  The idea is to use the rates of false positives and true positives on an x-y plane and to have x values represent the rates of false positives, and y values represent the rates of true positives.  The rate for a particular model can be plotted as a point on the ROC curve and the area under the curve (AUC) be used as a metric to determine the quality of the model with a point at (0,1) being optimal \cite{Posnett}.

These methods are used in a few of the papers we reviewed \cite{Rahman} \cite{Arisholm} \cite{Posnett}.  Some negatives have been pointed out about the ROC approach and its usefulness in certain circumstances.  One such negative is the fact that ROC curve approaches have "an overly optimistic view of an algorithm's performance if there is a large skew in the class distribution".  \cite{Davis}  Other papers mention the fact that both ROC/AUC approaches and confusion matrix based approaches in general do not address the whether a particular fault prediction methodology can pinpoint the source of the faults or not.  Since knowing where to find errors is just as important or more important than knowing whether errors exist or not several papers find ROC/AUC insufficient as an evaluation metric \cite{Posnett} \cite{Arisholm} \cite{Rahman}.

@@

The basic implementation of the metric is a set of two curves on an x-y plane that has a percentage of faults as the y-axis, and the percentage of LOC included in classes selected to focus verification as the x-axis.  Classes are ranked according to their likelihood of having defects, first by the model, and next by the size of the class in case of ties.  The graph has a baseline of $y=x$ which is essentially the assumption that the percentage of faults will be equivalent to the percentage of lines of code inspected, this is done using a random ranking of the classes.  On the same graph is the cost effectiveness curve which is the actual percentage of faults given the percentage of LOC of classes selected to focus verification according to the ranking determined by the model.

 Arisholm et al use an area calculation that is normalized to be a proportion of the optimal area under the curve.  To find an approximation of the optimal cost effectiveness they use a ranking that ranks the most error filled classes highly and then create a cost effectiveness line according to that ranking.  The actual calculation is\\ $CE_{\pi} = (CE_{pi}(model) - CE_{pi}(baseline))/$\\ $(CE_{pi}(optimal) - CE_{pi}(baseline))$  Other papers have used a simpler calculation of the area under the cost effectiveness curve, or AUCCE \cite{Posnett}.  The same concept is also used by Rahman et al under the name AUCEC \cite{Rahman}.

@@

\subsection{Discussion}
It seems that Arisholm's contribution to the community with Cost Effectiveness back in 2010 has provided a better metric to evaluate fault prediciton models going forward.  Seeing as the point of fault prediction should be to build tools that can be used in the real world for real projects, injecting the realism that CE brings to the table seems to be totally appropriate in going forward.  Even though that is viewed as the case by some in the community, confusion matrix based approaches and the related ROC curve concept are seemingly going nowhere.  These approaches will continue to be important in evaluating models until something better comes along.

@@

This section could also be labeled metrics, as it is in many places throughout the literature on this topic, but to not confuse it and the previous section on evaluation metrics we have chosen to label it features.  The main reasoning for this is the fact that metrics are actually used as features in Machine Learning algorithms and not actually as metrics for comparison of one method versus another.  The Radjenovic paper \cite{Radjenovic} is a fairly exhaustive paper with relation to metrics/features in fault prediction.  Radjenovic came up with three metric categories to discuss in their literature review, and we will stick with those same categories in relation to the papers we reviewed.  The categories are: Traditional, Object-Oriented, and Process.  Some of the papers we reviewed defy this categorization and use metrics that are either one offs or are hybridized to such a degree that they should be explained on their own.

@@

These are metrics that relate to complexity (ie McCabe or Halstead calculations) and lines of code.  A good number of papers we reviewed used these metrics as features \cite{Posnett} \cite{Vandecruys} \cite{Bird}.  There is considerable discussion in terms of whether these sorts of metrics provide good quality models or not.  Hall et al indicate that in their review that models using only static code metrics that are complexity based have poor performance, but that Lines of Code based models tend to be useful \cite{Hall}.  Radjenovic et al indicate that LOC based methods have no strong evidence behind them in terms of faults furthermore they state that smaller studies in general have given more weight to LOC and size metrics than larger studies, because of that they rated the effectiveness of the metric as "moderate"\cite{Radjenovic}.  On complexity metrics Radjenovic states that these metrics are reasonable, but that "others are better"\cite{Radjenovic}.

@@

Object oriented metrics seem to have been dominated by the metrics presented by Chidamber and Kemerer \cite{Chidamber} \cite{DAmbros}.  These metrics include things like number of children(NOC), coupling between classes (CBO), or lack of cohesion of methods (LCOM).  Object oriented metrics were used in only one of our papers, Arisholm et al, and used there really only as a comparison metric\cite{Arisholm}.  In terms of evaluation of their success or failure Radjenovic et al indicate that OO metrics are useful but that there is some debate about whether OO metrics and size metrics are correlated and that further work is needed in that area  \cite{Radjenovic}.  Hall et al state that OO and LOC are actually on pretty equal footing and that OO provides better performance than source code metrics \cite{Hall}.

@@

Process metrics relate to things like number of developers, code churn, number of commits, features, etc.  Process metrics are mostly mined from source code management systems like Git, and also bug tracking and issue tracking systems like Jira.   These metrics have a strong following in the fault prediction community and are well represented in our papers \cite{Posnett} \cite{Bird} \cite{Arisholm} \cite{Rahman}.  Rahman et al particularly only used a set of process metrics while the other papers mentioned used some sort of combination of process and other metrics.

There is some dispute between Radjenovic and Hall with regards to process metrics, with Hall suggesting that their performance was the worst out of everything they had examined where Radjenovic considers process metrics to be promising and that they are deserving of further study and validation while additionally stating that they provide superior post-release fault prediction \cite{Hall} \cite{Radjenovic}.

Another discussion of the strength of process metrics can be found in a 2013 paper by Rahman where he and Devanbu examine "How, and Why, Process Metrics are better"\cite{Rahman13}.  Based on the title it is fairly clear where Rahman and Devanbu come out on this, but the main thrust of their argument is that process metrics do not suffer from the stasis that code metrics do suffer from.  The idea is that between releases code metric based models lose relevancy as the distribution of defects in the project changes.  Further Rahman indicates that this assessment is geared towards situations in which AUC and Cost-Sensitive evaluation methods are being used.

Process metrics were also used by Zhang et al \cite{Zhang2014} to build a successful universal defect prediction model. This reaffirms the feature set as generalizable to other projects when performing cross-project defect prediction.

\subsection{Organizational Structure}
This is an approach that was proposed by Nagappan et al at Microsoft Research \cite{Nagappan}.  The metrics included a set of 8 measures of organizational complexity: Number of engineers, Edit Frequency, Depth of Master Ownership, Percentage of Org contributing to development, Overall Organization Ownership, and Organization Intersection Factor.  They used these metrics to create a fault prediction model and compared its performance in Precision and recall against a set of OO, Traditional, and Process metrics.  For Windows Vista they show that Organizational metrics are superior to the other types of metrics available.  As mentioned in the paper there are questions about whether this approach would work outside Microsoft or with a smaller project.  
Naggapan and Bird produced another paper in the next year using organizational metrics again with a bit of a twist in looking at whether distributed development had an effect on software quality \cite{Bird}.  This paper added an additional metric of the actual location of the members of teams working on Windows Vista with levels starting at the same building and growing to the point of developers working at locations across the globe from one another.  Organizaitonal metrics as well as a set of process and traditional metrics were used in conjunction with the distribution metric seemingly out of surprise that there was little difference between distributed projects and more local projects.  The idea was to try to prove that there was not in fact some correlation between the other metrics they looked at and the performance of teams across long distances.  They found that in fact there was no difference and that distributed development within one company was possible without sacrificing quality.
